### 2021-02-25 evaluation.tex
Fix a citation of TPTP

The problem library \acrshort{tptp}~v7.4.0 \cite{10.1007/978-3-030-29436-6_29}
was used as the source of problems for training and evaluation of the recommender,
offering a total of \num{17053} \gls{fol} problems.
We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$.

>>>>

The problem library \acrshort{tptp}~v7.4.0 \cite{Sutcliffe2017}
was used as the source of problems for training and evaluation of the recommender,
offering a total of \num{17053} \gls{fol} problems.
We denote the set of all the problems available for training and evaluation as $\ProblemsTptp$.
